### 2017-03-12 CO750-ApproximationAlgorithmsTopics/assignments/assignment_02.tex
writing up 3b

>>>>

We make an observation about optimal solutions to $(\overline{IP})$ which contain a $0$-valued edge. This will lead us to an approximation algorithm with a better bound than the one found in $3(a)$.
\begin{lemma}\label{lemma:0edge}
Let $x$ be an optimal solution $(\bar{IP})$. If there exists $v_iv_{i+1} \in E(G)$ such that $x(v_iv_{i+1}) = 0$ then for all $v_jv_{j+1} \in E(G)$
$$x(v_jv_{j+1}) = f(P(i+1, \ell)),$$
where $\ell = j-(i+1)$. Recall that $P(i+1, \ell)$ is the $\ell$ length path starting at $i+1$. In this case $P(i+1,\ell)$ is the path joining $v_{i+1}$ to $v_j$ avoiding $v_i$ and $v_{j+1}$. 
For each $v_jv_{j+1} \neq v_iv_{i+1} \in E(G)$ let $P(v_jv_{j+1}) = P(i+1, \ell)$ where $\ell = j-(i+1)$. Let $e_j \in E(G)$.  Since $x$ is feasible and $x(v_iv_{i+1}) = 0$,
$$f(P(e_j)) \leq x(\delta(P(e_j))) = x(e_j) + x(v_iv_{i+1}) = x(e_j).$$
Suppose for a contradiction there exists $e_j = v_{j}v_{j+1} \in E(G)$ such that
$$f(P(e_j)) < x(e_j).$$
 Let $x' \in \Z^{|E|}$ we given by
$$x'(e) = \begin{cases}
x(e), &\text{ if $e\neq e_j$} \\
f(P(e_j)), &\text{if $e=e_j$}. 
We claim that $x'$ is feasible for $(\overline{IP})$. By the feasibility of $x$, we need only check cut constraints involving $e_j$. Let $P \in \cP$ such that $e_j \in \delta(P)$. Let $e$ be the other edge in $\delta(P)$. If $e = v_iv_{i+1}$ then $P = P(i+1, \ell)$ or $P = V\backslash P(i+1, \ell)$. In either case $f(P) = x(e_j)$. So we may assume $e \neq v_iv_{i+1}$. Then either $v_i, v_{i+1} \in P$ or $v_i, v_{i+1} \in V\backslash P$. By the symmetry of $f$ we may assume $v_i, v_{i+1} \in P$ (otherwise proceed by replacing $P$ with $V\backslash P$). Thus since $v_i,v_{i+1} \in P$ and $e_j \in \delta(P)$, we have either $P(e_j) \subseteq P$ or $(V\backslash P(e_j)) \subseteq P$. Again by symmetry we may assume $P(e_j) \subseteq P$. Similarly $(V\backslash P(e)) \subseteq P$. In fact,
$$P = P(e_j) \cup (V\backslash P(e)).$$
Hence we have
f(P) &\leq f(P(e_j)) + f(V\backslash P(e)) &\text{by subadditivity}
\\
&= f(P(e_j)) + f(P(e)) &\text{ by symmetry} \\
&\leq f(P(e_j)) + x(\delta(P(e))) &\text{by feasibility of x} \\
&= f(P(e_j)) + x(e) + x(v_iv_{i+1}) \\
&= f(P(e_j)) + x(e) \\
&= x'(e_j) + x'(e) &\text{by definition of $x'$} \\
&= x'(\delta(P)).
Thus $x'$ is feasible. But 
\sum_{e\in E} c(e) x(e) &= c(e_j)x(e_j) + \sum_{e\in E\backslash\{e_j\}} c(e)x(e) \\
&> c(e_j)x'(e_j) +  \sum_{e\in E\backslash\{e_j\}} c(e)x(e) &\text{by contradiction hypothesis and our choice of $x'$} \\
&= c(e_j)x'(e_j) + \sum_{e\in E\backslash\{e_j\}} c(e)x'(e) &\text{by our choice of $x'$} \\
&= \sum_{e\in E} c(e) x'(e),
contradicting the optimality of $x$.
This lemma tells us precisely how to construct optimal solutions to $(\overline{IP})$ in the presence of $0$-valued edges.
